---
title: "The Mead Hall"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Data | Culture | History

```{r introduction, echo=FALSE}
library(fontawesome)

```

`r fa("dragon", fill = "steelblue")` Hello and welcome! My name is **Sarah Cole.**

`r fa("magnifying-glass-chart", fill = "blue")` I am a researcher with over **10 years of experience** in qualitative and quantitative data analysis.

`r fa("people-carry-box", fill = "green")` The best part of my jobs has been helping organizations in the public, private, and nonprofit sectors to collect and analyze the data for decision making.

`r fa("pen-to-square", fill = "black")` I have experience in various work environments: government contracting (USAID and the Department of Commerce), public-private partnerships (the Maine International Trade Center), and nonprofits (Democracy Fund, the Carter Center).

`r fa("archway", fill = "red")` As the daughter of two public school educators, I am always looking for opportunities to learn and serve. Topics I am particularly interested in include democracy, elections, international trade, and postcolonialism, especially in the Middle East.

`r fa("book", fill = "orange")` Talk to me about your favorite books! I have been on a sci-fi/ fantasy/ speculative fiction kick these last few years, and I'll always pick up a nonfiction book on an interesting subject.

And because the [fontawesome](https://rstudio.github.io/fontawesome/articles/icon-reference.html) package is amazing, here are some other icons matching my vibe:
`r fa("mountain-city", fill = "black")` `r fa("mug-hot", fill = "black")` `r fa("tree", fill = "black")` `r fa("spaghetti-monster-flying", fill = "black")`


### Look upon my works ye mighty and despair!

For they are mostly no longer funded.

<br>
<br>

<span style="color:blue">*Free tip of the day, for anyone wanting to use GitHub Pages and RMarkdown:*</span> you can easily convert the Rmd documents to md documents by including the following "output: github-document" at the top of the document, like so:

```{r github pages, eval=FALSE, echo=TRUE}
---
title: "Insert fun title here!"
output: github-document
---
  
```
