---
title: "Sarah Cole"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Data | Culture | History

```{r introduction, echo=FALSE}
library(fontawesome)

```

`r fa("dragon", fill = "purple")` Hello and welcome! My name is **Sarah Cole.**

`r fa("magnifying-glass-chart", fill = "blue")` I am a researcher with over **10 years of experience** in qualitative and quantitative data analysis.

`r fa("people-carry-box", fill = "green")` The best part of my jobs has been helping organizations in the public, private, and nonprofit sectors to **collect and analyze data for decision making.**

`r fa("pen-to-square", fill = "black")` I have experience in various work environments: **federal government contracting** (USAID and the Department of Commerce), **state-level public-private partnerships** (the Maine International Trade Center), and **domestic and international nonprofits** (Democracy Fund, the Carter Center).

`r fa("archway", fill = "red")` As the daughter of two public school educators, I am always looking for opportunities to **learn and serve**. Topics I am particularly interested in include democracy, elections, international trade, and postcolonialism, especially in the Middle East.

`r fa("book", fill = "orange")` Talk to me about your **favorite books**! I have been on a sci-fi/ fantasy/ speculative fiction kick these last few years, and I'll always pick up a nonfiction book on an interesting subject.

And because the [fontawesome](https://rstudio.github.io/fontawesome/articles/icon-reference.html) package is amazing, here are some other icons matching my vibe:
`r fa("mountain-city", fill = "black")` `r fa("mug-hot", fill = "black")` `r fa("tree", fill = "black")` `r fa("spaghetti-monster-flying", fill = "black")`

**Feel free to browse my publications and visualizations (vizzes), available on the left-hand side bar. The blog is still under construction - stay tuned!**