---
title: "blog under construction"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r introduction, echo=FALSE}
library(fontawesome)

```

<br>
<br>
<br>
<br>

**What are you doing here?** 

**Go back to the [main page](https://scole024.github.io/the-mead-hall/).**

**I think you're lost.**

**Nothing to see here.** `r fa("face-meh-blank", fill = "black")`

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>


**You're still here?!**

**You're a persistent little fella aren't you.**`r fa("person-hiking", fill = "black")`

**The blog is under construction!!** `r fa("person-digging", fill = "black")`

**Go bother Sarah and peer pressure her to hurry up and write.**

**You can probably ply her with a cup of coffee or something.**

**Oh and remind her that it's better to publish something imperfect than nothing at all.**

**Now, shoo!!** `r fa("person-through-window", fill = "black")`

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>


**I told you, go away!! Or I shall taunt you a second time!!** `r fa("far fa-chess-knight", fill = "black")`